---
title: "Data_import"
output: github_document
---


```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
library(janitor)
library(readxl)
library(haven)
```

This documnet will show how to import data. 

## Import the FAS Litters CSV

* Get rid of characters, lower case, replace space with underscore
* clean_name is the only one function in the janitor so I don't need library actually. It works when there are multiple packages use the same function name
```{r}
litters_df = read_csv("data_import_examples/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```


## Look at the dataset 
head(litters_df)
tail(litters_df,10)
```{r eval = FALSE}
view(litters_df)

```

## Learning Assessment 
```{r}
pups_df = read.csv("data_import_examples/FAS_pups.csv")
#read.csv("~/Desktop/data_wranging_i/data/FAS_litters.csv")
pups_df = janitor::clean_names(pups_df)

```

## Look at read_csv options 
col_names and skip 
```{r}
litters_df = read_csv(
  file = "data_import_examples/FAS_litters.csv",
  col_names = FALSE,
  skip = 1
)
```
what about missing values
```{r}
litters_df = 
  read_csv(
    file = "data_import_examples/FAS_litters.csv",
    na = c("NA","",".")
  )

litters_df = janitor::clean_names(litters_df)
pull(litters_df, gd0_weight)

```
what if we code `group` as a factor variable?
```{r}
litters_df = 
  read_csv(
    file = "data_import_examples/FAS_litters.csv",
    na = c("NA","","."),
    col_types = cols(
      Group = col_factor()
    )
  )
```

## Import an excel file

import MLB 2011 summary data
```{r}
mlb_df = read_excel("data_import_examples/mlb11.xlsx", sheet = "mlb11")

```

## Import SAS data
```{r}
pulse_df = read_sas("data_import_examples/public_pulse_data.sas7bdat")
```

## Never use read.csv()
```{r}
litters_df = read.csv("")
litters_df$L
```
## Never do this either: 
should not take stuff out. 
```{r}
litters_df$`Litter Number`

```



